FocalGstar

### 2017-06-15 analysis.Rmd
Updated images to my imagination

@@

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[up]),
     xlab = "Zoom level")

@@

@@

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[down]),
     xlab = "Zoom level")

@@

@@

@@

mean <- aggregate(d3$Up, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Up, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Up, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Up, by = list(d3global$Z + 1), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
mtext("CI: ??? TODO ???", line = -1, adj = .98)

mean <- aggregate(d3$Down, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Down, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Down, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Down, by = list(d3global$Z + 1), sd)
plot(NA, 
     ylab = expression(SoH^Down),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
mtext("CI: ??? TODO ???", line = -1, adj = .98)
```

@@

mean <- aggregate(d3$Up, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Up, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = "Focal matrix size",
     xlim = c(29, 137), ylim = c(0, 1))
plotCI(x = mean$Group.1, y = mean$x, uiw = sd$x, err = "y", pch = 20, slty = 3,
       scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))
mtext("CI: ??? TODO ???", line = -1, adj = .98)

mean <- aggregate(d3$Down, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Down, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Down),
     xlab = "Focal matrix size",
     xlim = c(29,137), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))
mtext("CI: ??? TODO ???", line = -1, adj = .98)
```

>>>>

# Slice plane for aggregation dimension SOH-UP

@@

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[up]),
     xlab = "Aggregation level")

@@

# Slice plane for aggregation dimension SOH-DOWN

@@

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[down]),
     xlab = "Aggregation level")

@@

# Slice plane for blur dimension SOH-UP

```{r blur-sohup, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
blur_soh <- read_csv("data/blur_soh.csv")

blur_soh %>% dplyr::select(Blur, "G*" = UpBlur) -> y1
blur_soh %>% dplyr::select(Blur, "Focal G*" = UpFocalBlur) -> y2

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[up]),
     xlab = "Weight matrix size")

# Slice plane for blur dimension SOH-DOWN

```{r blur-sohdown, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
blur_soh <- read_csv("data/blur_soh.csv")

blur_soh %>% dplyr::select(Blur, "G*" = DownBlur) -> y1
blur_soh %>% dplyr::select(Blur, "Focal G*" = DownFocalBlur) -> y2

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[down]),
     xlab = "Weight matrix size")

# X-Axis = Weight for whiskerplot, SOH Up and Down

@@

# X-Axis = Aggregation for whiskerplot

@@

mean <- aggregate(d3$Up, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Up, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Up, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Up, by = list(d3global$Z + 1), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
mtext("CI: FMsize + WMsize", line = -1, adj = .98)

mean <- aggregate(d3$Down, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Down, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Down, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Down, by = list(d3global$Z + 1), sd)
plot(NA, 
     ylab = expression(SoH^Down),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
mtext("CI: FMsize + WMsize", line = -1, adj = .98)
```

# X-Axis = Focal for whiskerplot

@@

mean <- aggregate(d3$Up, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Up, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = "Focal matrix size",
     xlim = c(29, 137), ylim = c(0, 1))
plotCI(x = mean$Group.1, y = mean$x, uiw = sd$x, err = "y", pch = 20, slty = 3,
       scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))
mtext("CI: WMsize + Aggregation", line = -1, adj = .98)

mean <- aggregate(d3$Down, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Down, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Down),
     xlab = "Focal matrix size",
     xlim = c(29,137), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))
mtext("CI: WMsize + Aggregation", line = -1, adj = .98)
```
